ERA5 Temperature and Humidity weekly data 2010-2024

### 2025-06-09 ERA5 data/1990-2020/ERA5_1990_2020.Rmd
update

Downloading temperature and humidity data from the cloud.

```{python}
# Importando a biblioteca do xarray e outras auxiliares
import xarray as xr
import numpy as np
import os
import matplotlib.pyplot as plt
from mpl_toolkits.axes_grid1.inset_locator import inset_axes
import datetime as dt
import pandas as pd
import geopandas
import regionmask
import seaborn as sns
import pytz
import warnings
warnings.filterwarnings("ignore")

>>>>

Downloading temperature and humidity data from the cloud.
You may run this code in python.

```{python}
# Libraries
import xarray as xr
import numpy as np
import os
import matplotlib.pyplot as plt
from mpl_toolkits.axes_grid1.inset_locator import inset_axes
import datetime as dt
import pandas as pd
import geopandas
import regionmask
import seaborn as sns
import pytz
import warnings
warnings.filterwarnings("ignore")

### 2025-06-09 ERA5 data/2010-2024/ERA5_2010_2024.Rmd
update

Downloading temperature and humidity data from the cloud.

```{python}
# Importando a biblioteca do xarray e outras auxiliares
import xarray as xr
import numpy as np
import os
import matplotlib.pyplot as plt
from mpl_toolkits.axes_grid1.inset_locator import inset_axes
import datetime as dt
import pandas as pd
import geopandas
import regionmask
import seaborn as sns
import pytz
import warnings
warnings.filterwarnings("ignore")

>>>>

Downloading temperature and humidity data from the cloud.
You may run this code in python.

```{python}
# libraries
import xarray as xr
import numpy as np
import os
import matplotlib.pyplot as plt
from mpl_toolkits.axes_grid1.inset_locator import inset_axes
import datetime as dt
import pandas as pd
import geopandas
import regionmask
import seaborn as sns
import pytz
import warnings
warnings.filterwarnings("ignore")
